\textbf{\Huge Maulana Abul Kalam Azad University of\\[10pt] Technology}

### 2017-05-27 SQL/SQL.tex
Modified SQL.tex
Signed-off-by: mouri11 <rohit.das950@gmail.com>

\usepackage{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{2}

@@

\begin{center}
\LARGE\textbf{\underline{INDEX}}
\end{center}
\thispagestyle{empty}
\begin{tabular}{|c|p{0.48\linewidth}|c|c|c|}
\textbf{Sl. No.}&\textbf{Particulars}&\textbf{Date}&\textbf{Page No.}&\textbf{Signature}\\[5pt] \hline
\\1.&Program to calculate average of cricket players.& 28/9/16 & 3 &\\ \hline
\\2.&Program to calculate cost for consumer.& 28/9/16 & 4 &\\ \hline
\\3.&Program to display votes received in election.& 28/9/16 & 5 &\\ \hline
\\4.&Program for operation on array elements.& 19/10/16 & 6 &\\ \hline
\\5.&Program to calculate factorial of a number.& 19/10/16 & 7 &\\ \hline
\\6.&Program to calculate sum of series$1+22+32+42+...$.& 19/10/16 & 7 &\\ \hline
\\7.&Program to add values of Complex no. objects.& 9/11/16 & 8 &\\ \hline
\\8.&Program to convert distances to inches and add.& 28/9/16 & 9 &\\ \hline
\\9.&Program for String class with different costructors.& 9/11/16 & 10 &\\ \hline
\\10.&Program to display unique roll of Student objects.& 9/11/16 & 10 &\\ \hline
11.&Program to swap values of objects using 'friend' function.& 9/11/16 & 11 &\\ \hline
\\12.&Program for operation on matrices.& 16/11/16 & 12 &\\ \hline
13.&Program to use overloaded operators on float numbers.& 16/11/16 & 14 &\\ \hline
\\14.&Program to compare two strings by '==' operator.& 16/11/16 & 15 &\\ \hline
\\15.&Program to implement current and savings a/c.& 23/11/16 & 16 &\\ \hline
\\16.&Previous program rewritten using constructors.& 23/11/16 & 18 &\\ \hline
\\17.&Program for an educational institution.& 23/11/16 & 20 &\\ \hline
\\18.&Program to implement a network.& 23/11/16 & 23 &\\ \hline
\\19.&Program to show overriding using 'virtual'.& 30/11/16 & 24 &\\ \hline
\\20.&Program to implement Shape class using 'virtual'.& 30/11/16 & 25 &\\ \hline
\\21.&Previous program rewritten without using 'virtual'.& 30/11/16 & 26 &\\ \hline
\\22.&Program to use template for an array.& 7/12/16 & 27 &\\ \hline
23.&Program to implement exception handling with multiple catch.& 7/12/16 & 28 &\\ \hline
\\24.&Program to implement rethrowing an exception.& 7/12/16 & 29 &\\ \hline
\\25.&Program to implement a generic vector.& 27/12/16 & 29 &\\ \hline
\end{tabular}
%\end{table}

@@

\subsection{List all the clients who are located in Mumbai.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name from client_master
where city='Mumbai'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
%\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q2.csv}
\end{figure}
\bigskip

>>>>

\usepackage[titles]{tocloft}
\cftsetindents{section}{0em}{2em}
\cftsetindents{subsection}{0em}{2em}
\renewcommand\cfttoctitlefont{\hfill\LARGE\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}
\setcounter{tocdepth}{10}
\setlength{\cftsubsecindent}{1cm}
\setlength{\cftsubsecnumwidth}{3em}
\addto\captionsenglish{%  
  \centering\renewcommand{\contentsname}{INDEX}%
}

@@

\tableofcontents
\break

@@

\subsection{List all the clients who are located in Mumbai.}
\underline{Query:}
\begin{lstlisting}[showstringspaces=false]
select name from client_master
where city='Mumbai'
\end{lstlisting}
Output:
\begin{figure}[H]
\centering
\csvautotabular{/home/mouri/DBMS2/DBMS/Week5/q2.csv}
\end{figure}
\bigskip
